Systematic review of outbreak response models: data analysis

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis_by_collab_type.Rmd
Fixed some paths

#resolve package function conflicts
conflict_prefer('filter', 'dplyr')
conflict_prefer('select', 'dplyr')
conflict_prefer('kable', 'knitr')
```

```{r echo=FALSE, include=FALSE, eval=FALSE}
# Source the script that cleans the raw data
# Load the script that cleans the data and saves it; 
# this should be run each time, just in case something has changed in the data cleaning process;
# The script clears the environment after cleaning the data
#source('./data_cleaning/orv_models_review_data_cleaning.R')
```

```{r echo=FALSE, include=FALSE}
# Load the cleaned data 
long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')

#The cleaned data without citations
compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')

@@

# The data with citations 
compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/final_data/cleaned_data/compact_data_with_citation_keys_cleaned.rds'))

>>>>

#resolve package function conflicts
conflict_prefer('filter', 'dplyr')
conflict_prefer('select', 'dplyr')
conflict_prefer('kable', 'knitr')

data_dir <- "../data"
```

```{r echo=FALSE, include=FALSE, eval=FALSE}
# Source the script that cleans the raw data
# Load the script that cleans the data and saves it; 
# this should be run each time, just in case something has changed in the data cleaning process;
# The script clears the environment after cleaning the data
source(file.path('orv_models_review_data_cleaning.R'))
```

```{r echo=FALSE, include=FALSE}
# Load the cleaned data 
long_data <- read_rds(file.path(data_dir, 'review_data_long_cleaned.rds'))

#The cleaned data without citations
compact_data_init <- read_rds(file.path(data_dir, "review_data_compact_cleaned.rds"))

@@

# The data with citations 
compact_data_with_citation_keys_init <- read_rds(file.path(data_dir, "compact_data_with_citation_keys_cleaned.rds"))
